---
title: "chap12_using_color_in_plots"
author: "J.H AHN"
date: '2022 1 11 '
output: 
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
library(gcookbook)
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(echo = TRUE)
```

<br>
<br>

### 12.1 Setting the colors of objects

<br>

<br>

```{r fig_12_1}
fig_12011 <- 
  mtcars %>% 
  ggplot(aes(x = wt, y = mpg)) +
  geom_point(color = "#B22222")

library(MASS)
fig_12012 <- 
  birthwt %>% 
  ggplot(aes(x = bwt)) +
  geom_histogram(fill = "#8B0000", color = "#000000")

fig_12011 + fig_12012

```


<br>
<br>

### 12.2 Mapping variables to colors

<br>

<br>

```{r fig_12_2}
fig_12021 <- 
  cabbage_exp %>% 
  ggplot(aes(x = Date, y = Weight, fill = Cultivar)) + 
  geom_bar(stat = "identity", position = "dodge", color = "#000000")

fig_12022 <- 
  mtcars %>% 
  ggplot(aes(x = wt, y = mpg, color = cyl)) +
  geom_point()

fig_12021 + fig_12022

```


<br>

```{r fig_12_3}
mtcars %>% 
  ggplot(aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point()

```


<br>
<br>

### 12.3 Using a different palette for a discrete variable

<br>

<br>

```{r fig_12_4}
fig_12041 <- 
  uspopage %>% 
  ggplot(aes(x = Year, y = Thousands, fill = AgeGroup)) +
  geom_area(position = position_stack(reverse = TRUE))

fig_12042 <- 
  uspopage %>% 
  ggplot(aes(x = Year, y = Thousands, fill = AgeGroup)) +
  geom_area(position = position_stack(reverse = TRUE)) +
  scale_fill_brewer(palette = "Blues")

fig_12041 + fig_12042

```


<br>

`scale_color_hue()`에서 h = range of hues to use, in [0, 360], c = chroma (intensity of colour), maximum value varies depending on combination of hue and luminance., l = luminance (lightness), in [0, 100]를 의미한다.  

<br>

```{r fig_12_5}
fig_12051 <- 
  heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = sex)) +
  geom_point()

fig_12052 <- 
  heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = sex)) +
  geom_point() + 
  scale_color_hue(l=45)

fig_12051 + fig_12052

```


<br>

```{r fig_12_6}
library(RColorBrewer)
display.brewer.all()

```


<br>

```{r fig_12_7}
uspopage %>% 
  ggplot(aes(x = Year, y = Thousands, fill = AgeGroup)) +
  geom_area(position = position_stack(reverse = TRUE)) +
  scale_fill_brewer(palette = "Oranges")


```


<br>

```{r fig_12_8}
fig_12081 <- 
  uspopage %>% 
  ggplot(aes(x = Year, y = Thousands, fill = AgeGroup)) +
  geom_area(position = position_stack(reverse = TRUE)) +
  scale_fill_grey()

fig_12082 <- 
  uspopage %>% 
  ggplot(aes(x = Year, y = Thousands, fill = AgeGroup)) +
  geom_area(position = position_stack(reverse = TRUE)) +
  scale_fill_grey(start = 0.7, end = 0)

fig_12081 + fig_12082

```


<br>
<br>

### 12.4 Using a manually defined palette for a discrete variable

<br>

<br>

```{r fig_12_9}
fig_12091 <- 
  heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = sex)) +
  geom_point() +
  scale_color_manual(values = c("#8B0000", "#191970"))

fig_12092 <- 
  heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = sex)) +
  geom_point() +
  scale_color_manual(values = c("#90ee90", "#FFCBCB"))


fig_12091 + fig_12092

```


<br>
<br>

### 12.5 Using a colorblind-friend palette

<br>

<br>

```{r fig_12_10}
cb_palette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
                "#0072B2", "#D55E00", "#CC79A7")

uspopage %>% 
  ggplot(aes(x = Year, y = Thousands, fill = AgeGroup)) +
  geom_area(position = position_stack(reverse = TRUE)) + 
  scale_fill_manual(values = cb_palette)


```


<br>

경우에 따라 검은색 대신에 회색을 써도 됨.  

<br>

```{r}
c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442","#0072B2", "#D55E00", "#CC79A7")
scales::show_col(c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442","#0072B2", "#D55E00", "#CC79A7"))

```


<br>
<br>

### 12.6 Using a manually defined palette for a continuous variable

<br>

<br>

```{r fig_12_12}
fig_12121 <- 
  heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = weightLb)) +
  geom_point() +
  scale_color_gradient(low = "#000000", high = "#FFFFFF") + 
  labs(subtitle = "with scale_color_gradient")

fig_12122 <- 
  heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = weightLb)) +
  geom_point() +
  scale_color_gradient2(low = scales::muted("#FF0000"), 
                        mid = "#FFFFFF",
                        high = scales::muted("#0000FF"),
                        midpoint = 110) + 
  labs(subtitle = "gradient with mid color")

fig_12123 <- 
   heightweight %>% 
  ggplot(aes(x = ageYear, y = heightIn, color = weightLb)) +
  geom_point() +
  scale_color_gradientn(colors = c("#FF0000", "#FFA500", "#FFFF00", "#FFFFFF")) +
  labs(subtitle = "gradient with n colors")


fig_12121 + fig_12122 + fig_12123 + plot_layout(ncol = 2)

```


```{r}
scales::show_col(c(scales::muted("#FF0000"), "#FF0000", scales::muted("#0000FF"), "#0000FF"))

```


<br>
<br>

### 12.7 Coloring a shaded region based on value

<br>


<br>

```{r}
cb <- 
  climate %>% 
  subset(Source == "Berkeley") %>% 
  mutate(valence = case_when(Anomaly10y >= 0 ~ "pos", TRUE ~ "neg"))

cb

```


<br>

자세히 보면 0부근에 두 색이 겹쳐져 있는 것을 발견할 수 있다.  
두 색깔 영역이 각각의 데이터로 연결된 하나의 다각형으로 묶여져 있어 발생하는 현상이다.  
이런 현상을 방지하기 위해서 `approx()`를 사용하여 interpolation 시켜줘야 한다.  

<br>

```{r fig_12_13}
cb %>% 
  ggplot(aes(x = Year, y = Anomaly10y)) +
  geom_area(aes(fill = valence)) +
  geom_line() +
  geom_hline(yintercept = 0)

```


```{r}
# approx() return a list with x and y vectors
interp <- approx(cb$Year, cb$Anomaly10y, n = 1000)

# put in a data frame and recalculate valence
cbi <- data.frame(Year = interp$x, Anomaly10y = interp$y)

cbi <- 
  cbi %>% 
  mutate(valence = case_when(Anomaly10y >= 0 ~ "pos", TRUE ~ "neg"))

cbi

```


<br>

```{r}
cbi %>% 
  ggplot(aes(x = Year, y = Anomaly10y)) +
  geom_area(aes(fill = valence), alpha = 0.4) +
  geom_line() +
  geom_hline(yintercept = 0) +
  scale_fill_manual(values = c("#CCEEFF", "#FFDDDD"), guide = "none") +
  scale_x_continuous(expand = c(0,0))


```


<br>
<br>
<br>


**END**


<br>
<br>
<br>